\chapter{Top level description}
This chapter will give a high level view of main MPCEE components with their
roles and their code location. MPCEE is written in C code with some part in
MMDSP assembly. It's written using NMF component technology.
\section{Scheduler}
Scheduler module role is to accept new NMF reactions posting and then to
execute them according to their priorities. Reactions can be post from either host code,
other MMDSP core or betweens NMF components if they are connected with
asynchronous bindings. When there is no more reactions to execute scheduler is
also responsible to call power module to save power.

Code is mainly located in :
\begin{itemize}
  \item rtos/hybrid/hybrid/*
  \item rtos/common/src/lowscheduler.c
  \item rtos/common/inc/lowscheduler.h
\end{itemize}

\section{Communications}
Communication module role is to provide communication primitive to allow posting
of reactions between host and MMDSP but also between two MMDSP.

Code is mainly located in :
\begin{itemize}
  \item communication/*
  \item semaphores/*
\end{itemize}

\section{Services}
Services module role is to allow remote execution of code from CM driver to
perform components and NMFEE maintenance operations.

Code is mainly located in :
\begin{itemize}
  \item communication/src/services.c
\end{itemize}

\section{Power}
Power module role is to allow to reduce power when there is no more reactions to
execute. There is two level of low power mode implemented.

Code is mainly located in :
\begin{itemize}
  \item rtos/hybrid/hybrid/src/scheduler.c@METH(enter)
  \item sleep/ulp/*
  \item sleep/prcmu/*
\end{itemize}

\section{Interrupts dispatcher}
Interrupt module role is to allow the dispatch of interrupt for NMF components
that provide interrupt handler.

Code is mainly located in :
\begin{itemize}
  \item rtos/itdispatcher/nofpu/*
\end{itemize}

\section{Trace}
Trace module role is to trace component execution to help debugging. It also a
printf like api for code debugging.

Code is mainly located in :
\begin{itemize}
  \item rtos/trace/xti/*
  \item rtos/common/src/service.c
\end{itemize}

\section{Startup}
Startup module role is to boot MMDSP either after a cold boot or after a deep
sleep wake-up. It also allow to catch call to non binding interface and to
generate a panic call.

Code is mainly located in :
\begin{itemize}
  \item rtos/vector/*
\end{itemize}

\section{Panic}
Panic module role is to halt mmdsp and to signal CM driver when a panic occur.
Source of panic is either internal to MPCEE or call from user code.

Code is mainly located in :
\begin{itemize}
  \item rtos/common/src/service.c
\end{itemize}
